\cvsection{Experience}
\begin{cventries}
  \cventry
  	{Undergraduate Research Assistant}
    {University Houston}
    {Stafford, TX, USA}
    {Jan. 2017 - Sep. 2017}
    {
      \begin{cvitems}
        \item {Working on equation discovery, machine learning concepts for physics.}
        \item {\textbf{Supervisor:} Dr. Ricardo Vilalta}
      \end{cvitems}
    }
  \cventry
  	{Chair~~\&~~Vice Chair~~\&~~Lab Leader~~\&~~Senator}
    {ACM (Association for Computing Machinery)}
    {Stafford, TX, USA}
    {Sep. 2015 - PRESENT}
    {
      \begin{cvitems}
        \item {Increase campus involvement with Computer Science as Student Chapter Chair through organizing daily meetings, events, and connecting students to industry knowledge and professionals.}
        \item {Plan events including company site visits, guest industry speakers, Hackathons, Capture the Flag competitions, and professional development events for the community.}
        \item {Expand knowledge and skills across fields for both broad and in-depth learning by working with specific fields of
Computer Science and industry professionals}
		\item{Represent the organization as Senator in weekly Student Government Association meetings. \textit{(Former Position)}}
       	\item{ Lead the iOS Development Lab within the ACM chapter, and serve as member of Artificial Intelligence Lab \& Algorithms lab. \textit{(Former Position)}}
      \end{cvitems}
    }
    \cventry
  	{Teaching Assistant}
    {Momentum Learning}
    {Houston, TX, USA}
    {June 2017 - July 2017}
    {
      \begin{cvitems}
        \item {Was working with Mr.Zhang to teach Java Programming to 16 kids from 10 to 18.}
        \item {\textbf{Tools:} Java, Eclipse}
        \item {\textbf{GitHub Repository:} \href{https://github.com/BedirT/Momentum\_Java\_Class}{https://github.com/BedirT/Momentum\_Java\_Class}}
      \end{cvitems}
    }
    \cventry
  	{Software Developer + Designer}
    {MLRPro - Machine Learning Resume Processor}
    {Houston, TX, USA}
    {April 2017}
    {
      \begin{cvitems}
        \item {A tool that evaluates the submitted resume, according to data that used to feed the machine learning algorithm behind the scene, and gives result that if the submitted resume is qualify enough to apply top companies.}
        \item {\textbf{Tools:} Python, Flask, HTML/CSS, Adobe Illustrator}
        \item {\textbf{Website:} \href{http://mlrpro.com}{http://mlrpro.com} }
        \item {\textbf{GitHub Repository:} \href{https://github.com/MichaelMMeskhi/MLRP}{https://github.com/MichaelMMeskhi/MLRP}}
      \end{cvitems}
    }
  \cventry
  	{Developer~~\&~~Graphic Designer}
    {Scholar Development Center}
    {Houston, TX, USA}
    {February 2015}
    {
      \begin{cvitems}
        \item {Led, organized, and implemented a project that helped students achieve increased awareness for academic success, encouraged career readiness, and improved career opportunities through mentor program.}
        \item {\textbf{Tools:} Moodle System, Adobe Illustrator}
      \end{cvitems}
    }
    \cventry
  	{Graphic Designer}
    {Connect Aid - \tiny{Web Application}}
    {Houston, TX, USA}
    {October-December 2015}
    {
      \begin{cvitems}
        \item {Connect Aid is a non-profit online platform that makes specific and flexible volunteering possible.}
        \item {\textbf{Tools:} Adobe After Effect, Adobe Illustrator}
      \end{cvitems}
    }
    \cventry
  	{Developer~~\&~~Graphic Designer}
    {Recipe - \tiny{Mobile Application}}
    {Houston, TX, USA}
    {October-December 2015}
    {
      \begin{cvitems}
        \item {Worked in a team of four to develop an iOS application for people to find out what meal they can cook with the ingredients they have.}
        \item {\textbf{Tools:} Swift 2.0, Xcode, GitHub, Git, Adobe Illustrator, Adobe Photoshop}
      \end{cvitems}
    }
    \cventry
  	{Organizer~~\&~~Director~~\&~~Developer}
    {Algorithms ACM-ICPC Curriculum}
    {Stafford, TX, USA}
    {October-December 2015}
    {
      \begin{cvitems}
      	\item {\textbf{Tools:} C++, Java, C, Python, Git, Github}
        \item {Created a Curriculum that helps people study Algorithms, and prepare ACM-ICPC contest. Used already exist
information in addition to own explanation about the algorithm. Added questions about the topic and solutions.}
		\item{\textbf{Github Repository:}  \href{https://github.com/NAU-ACM/ACM-ICPC-Preparation}{https://github.com/NAU-ACM/ACM-ICPC-Preparation}}
      \end{cvitems}
    }
    
    {
    %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }
\end{cventries}
