 \documentclass[margin,line]{res}

\usepackage{hyperref}
\hypersetup{
   colorlinks,
   citecolor=black,
   filecolor=black,
   linkcolor=black,
   urlcolor=red
}

\usepackage{url}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

%if using pdflatex:
\setlength{\pdfpagewidth}{\paperwidth}
\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{M Bedir Tapkan \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{3in}p{3in}}
10708 79th Ave NW & \hfill {\it GitHub:}  \href{https://github.com/bedirT}{bedirT} \\
T6E 1S3, Edmonton, AB, Canada & \hfill {\it E-mail:}  \href{mailto:tapkan@ualberta.ca}{tapkan@ualberta.ca}\\
%& \hfill {\it Portfolio:}  \href{www.bedirtapkan.com}{www.bedirtapkan.com} \\
\end{tabular}


\section{\sc Research Interests}
Reinforcement Learning, 
Partially Observable Environments, \\
Policy Gradients, 
Deep Learning,
Dark Hex, 
Solving Games

\section{\sc Education}

 {\bf University of Alberta (UofA)}, Edmonton, AB, Canada\\
 {\em Computer Science} 
 \begin{list1}
 \item[] MsC, Computer Science, 2019 - \textit{Ongoing}
\end{list1}
\begin{list2}
\vspace*{.05in}
\item {\bf Supervisors:}  Martin Mueller, Ryan Hayward
\item {\bf Thesis Topic:}  ``Developing a state of the art player for Dark-Hex using Deep Reinforcement Learning. Solving Dark Hex in small board sizes.''
\end{list2}

{\bf North American University (NAU)}, Houston, Texas, USA\\
{\em Computer Science}  \hfill {\bf Overall-GPA: 3.79 - Major-GPA: 3.94}\\
\vspace{-.3cm}
\begin{list1}
\item[] B.S., Computer Science,  2015 - 2018
\end{list1}


\section{\sc Research Experience}

{\bf Undergraduate Research Assistant}

\vspace{-.3cm}
{\em University of Houston} \hfill {\bf January, 2017 - February, 2019}\\ 
\vspace{-.3cm}
\begin{list2}
\item \textbf{Supervisor:} Dr. Ricardo Vilalta
\item Transfer learning methods focused on finding a remedy on exploration/exploitation
\item Using meta-learning (and transfer learning) to help reinforcement learning models to achieve adaptivity through environment. 
\end{list2}

\section{\sc Teaching Experience}
{\bf Teaching Assistant}

\vspace{-.3cm}
{\em University of Alberta} \hfill {\bf August 2019 - Ongoing}\\
\begin{list2}
  \item TA for CMPUT 455: Search, Knowledge, Simulation under the supervision of Dr. James Wright. Helped marking, held office hours for helping students who needs further explanation on course material.

	\item TA for CMPUT 355: Algorithms and Puzzles under the supervision of Dr. Ryan Hayward. Helped marking and proctoring, held office hours for students to direct further questions about class material and contributed to the code base development for the class repository.
	
	\textbf{Tools:} Python, Git, Github
	\item TA for CMPUT 272: Formal Systems and Logic in Computing Science under the supervision of Lorna Stewart. Helped students understanding the material, marking, proctoring.
	
\end{list2}
\vspace*{.05in}

{\bf Teacher}

\vspace{-.3cm}
{\em Momentum Learning} \hfill {\bf January 2019 - July 2019}\\
\begin{list2}
\item Taught Python, Java and 3D classes to kids at age 9-15. Focused on fundamentals of programming, how to solve daily problems with certain tools in Computer Science.
\item \textbf{Tools:} Java, Python, TinkerCAD, Git, Github
\end{list2}
\vspace*{.05in}

\newpage
{\bf Instructor - Algorithms for ICPC}

\vspace{-.3cm}
{\em North American University} \hfill {\bf January 2018 - May 2018}\\
\begin{list2}
\item Taught basic to advanced algorithms, data structures, competitive programming basics, basic logic, math and coding to 12 students from freshman to senior using C++/Python, Git/Github. Prepared class curriculum, lesson plan, and homework assignments.
\item \textbf{Tools:} C++, Python, Git, Github
\end{list2}
\vspace*{.05in}

% \section{\sc Publications}
% Kocabas, F., {\bf Ergin, E.K}. (2016). Identification of small molecule binding pocket for inhibition of Crimean-Congo hemorrhagic fever virus OTU protease. {\em Turkish Journal of Biology}, 40:239-249.

\section{\sc Papers in preparation}

Peet-Pare, L., Aghakasiri, K., Tapkan, B., Sattarifard, A., Kohankhaki, F., White, M., Sokota, S. 2021. Using Heteroscedastic Regression to Identify Model Bias. {\em ICML}

%\section{\sc Conference Presentations}
%
% Kocabas, F., Ergin, E.K. 2016. Identification of small molecule binding pocket for inhibition of Crimean-Congo hemorrhagic fever virus OTU protease. Turkish Journal of Biology, 40:239-249.



\section{\sc Projects}

{\bf Anomaly Detection on CO2 levels in ISS} \hfill {\bf April 2018}\\
\vspace{-.3cm}
\begin{list2}
\item Created a tool to analyze anomalies on CO2 levels and clusterings inside International Space Station. Presented a poster and the tool in Wearable Technologies Workshop at NASA. Worked closely with a team in NASA. The presented software is currently used in ISS.
\item \textbf{Tools:} Python, Pytorch, JavaScript, Pandas, Numpy, Scikit, Flask
\end{list2}


{\bf MLRPro - Machine Learning Resume Processor} \hfill {\bf April 2017}\\
\vspace{-.3cm}
\begin{list2}
\item Created a tool that evaluates the submitted resume, according to the data that used to feed the ML systems, and gives result on companies given resume is qualified to apply. Worked with a team of 3.
\item \textbf{Tools:} Python, Pytorch, Scikit, Flask
\item \textbf{Repository:} \href{https://github.com/MichaelMMeskhi/MLRP}{https://github.com/MichaelMMeskhi/MLRP}
\end{list2}

{\bf ACM-ICPC Preparation Curriculum (Open-Source)} \hfill {\bf October-December 2015}\\
\vspace{-.3cm}
\begin{list2}
\item Created a curriculum to help preparation process of the international competition ACM-ICPC, to self study algorithms and data-structures and to get the underlying concepts of algorithms.
\item The curriculum is currently ranked in top 20 most popular open source courses on Github (\href{https://education.github.community/t/20-of-the-most-popular-courses-on-github/27832}{Article Link})
\item \textbf{Tools:} C++, Java, C, Python, Git, Github
\item \textbf{Repository:} \href{https://github.com/NAU-ACM/ACM-ICPC-Preparation}{https://github.com/NAU-ACM/ACM-ICPC-Preparation}
\end{list2}

\section{\sc Honors and Awards}

North American University: Exceptional Merit Scholarship, 2014-2019\\
North American University: President's Honor Roll , 2016-2018


\section{\sc Extracurricular Activities}
\begin{list2}
\item ACM NAU Chapter {\em \textbf{Chair, Vice Chair, Lab Leader, Senator}} \hfill {\bf 2015-2018}
\item Artificial Intelligence, ACM-ICPC, iOS Development, {\em \textbf{Member in ACM Labs}} \hfill {\bf 2015-2018}
\item NAU Communications Club, NAU Future Leaders Club, {\em \textbf{Graphic Designer}} \hfill  {\bf 2015-2018}
\item HackNAU - 2017 | 60+ Attendees hosted, {\em \textbf{Organizer \& Director}} \hfill {\bf 2017}
\item HackHouston 2017 Best Project Overall and Best Machine Learning Project, {\em \textbf{1$^{st}$ place}} \hfill  {\bf 2017}
\item Scholar Development Center | {\em \textbf{Organizer \& Director \& Co-founder}} \hfill {\bf 2016} 
\item iHackathon | 30+ Attendees hosted, {\em \textbf{Organizer \& Director}} \hfill {\bf 2016} 
\item NAU - Moonlight CTF 1, {\em \textbf{Organizer \& Co-Director}} \hfill {\bf 2016}
\item ACM-ICPC Regional Contest, {\em \textbf{18$^{th}$ place}} \hfill  {\bf 2016}
\end{list2}

\section{\sc Technical Skills} 
\begin{list2}
\item{\textbf{Expert:}\space Python, C++, PyTorch, Numpy, UNIX, GitHub, Adobe Illustrator}
\item{\textbf{Advanced:}\space C, R, Linux, Git, TensorFlow, Pandas, Scikit-Learn, Java, \LaTeX, SQL, Swift, Flask, Django, HTML/CSS, Adobe Photoshop}
\end{list2}

\section{\sc References} 
{\bf References available upon request}
% \begin{list2}
% \item Associate Prof. Dr. Ricardo Vilalta, Computer Science Department, University of Houston, Houston, TX, USA, \href{rvilalta@uh.edu}{rvilalta@uh.edu}
% \item Associate Prof. Dr. Kemal Aydin, Computer Science Department, Franklin University, Columbus, Ohio, USA, \href{kemal.aydin@franklin.edu}{kemal.aydin@franklin.edu}
% \item Prof. Dr. Serkan Dursun, Researcher at Marathon Oil, Houston, TX, USA \href{sdursun@hotmail.com}{sdursun@hotmail.com} 
% \end{list2}

\end{resume}
\end{document}
