\cvsection{Experience}
\begin{cventries}
  \cventry
  	{Undergraduate Research Assistant}
    {University of Houston}
    {Houston, TX, USA}
    {Jan. 2017 - Sep. 2017}
    {
      \begin{cvitems}
        \item {Worked on equation discovery, machine learning concepts for physics. Concepts related to system identification evaluated.}
        \item {\textbf{Supervisor:} Dr. Ricardo Vilalta}
      \end{cvitems}
    }
  \cventry
  	{Chair~~\&~~Vice Chair~~\&~~Lab Leader~~\&~~Senator}
    {ACM (Association for Computing Machinery)}
    {Stafford, TX, USA}
    {Sep. 2015 - PRESENT}
    {
      \begin{cvitems}
        \item {Increase campus involvement with Computer Science as Student Chapter Chair through organizing daily meetings, events, and connecting students to industry knowledge and professionals.}
        \item {Plan events including company site visits, guest industry speakers, Hackathons, Capture the Flag competitions, and professional development events for the community.}
        \item {Expand knowledge and skills across fields for both broad and in-depth learning by working with specific fields of
Computer Science and industry professionals}
		\item{Represent the organization as Senator in weekly Student Government Association meetings. \textit{(Former Position)}}
       	\item{ Lead the iOS Development Lab within the ACM chapter, and serve as member of Artificial Intelligence Lab \& Algorithms lab. \textit{(Former Position)}}
      \end{cvitems}
    }
    \cventry
  	{Software Developer + Designer}
    {MLRPro - Machine Learning Resume Processor}
    {Houston, TX, USA}
    {April 2017}
    {
      \begin{cvitems}
        \item {A tool that evaluates the submitted resume, according to data that used to feed the machine learning algorithm behind the scene, and gives result that if the submitted resume is qualify enough to apply top companies.}
        \item {\textbf{Tools:} Python, Flask, HTML/CSS, Adobe Illustrator}
        \item {\textbf{Website:} \href{http://mlrpro.com}{http://mlrpro.com} }
        \item {\textbf{GitHub Repository:} \href{https://github.com/MichaelMMeskhi/MLRP}{https://github.com/MichaelMMeskhi/MLRP}}
      \end{cvitems}
    }
    \cventry
  	{Organizer~~\&~~Director~~\&~~Developer}
    {Algorithms ACM-ICPC Curriculum}
    {Stafford, TX, USA}
    {October-December 2015}
    {
      \begin{cvitems}
      	\item {\textbf{Tools:} C++, Java, C, Python, Git, Github}
        \item {Created a Curriculum that helps people to study Algorithms, and prepare ACM-ICPC contest. Used information that already exist
 in addition to own explanation about the algorithms. Added questions about the topics and own solutions.}
		\item{\textbf{Github Repository:}  \href{https://github.com/NAU-ACM/ACM-ICPC-Preparation}{https://github.com/NAU-ACM/ACM-ICPC-Preparation}} 
      \end{cvitems}
    }
  \cventry
  	{Developer~~\&~~Graphic Designer}
    {Bulletin-NAU - \tiny{Mobile Application}}
    {Stafford, TX, USA}
    {December 2017}
    {
      \begin{cvitems}
        \item {Led, organized, and implemented a project that helps NAU students, staff, and professors to have better connection in between. An iOS messaging application that all NAU staff and students can see each other like email system, but it is an application with real-time updates on the database.}
        \item {\textbf{Tools:} Swift 4.0, Xcode, Firebase, GitHub, Git, Adobe Illustrator, Adobe Photoshop}
      \end{cvitems}
    }
    \cventry
  	{Developer~~\&~~Graphic Designer}
    {Recipe - \tiny{Mobile Application}}
    {Houston, TX, USA}
    {October-December 2015}
    {
      \begin{cvitems}
        \item {Worked in a team of four to develop an iOS application for people to find out what meal they can cook with the ingredients they have.}
        \item {\textbf{Tools:} Swift 2.0, Xcode, GitHub, Git, Adobe Illustrator, Adobe Photoshop}
      \end{cvitems}
    }
    \cventry
  	{Assistant Manager}
    {North American University - Chestnut Residence Hall}
    {Stafford, TX, USA}
    {Sep. 2017 - Current}
    {
      \begin{cvitems}
        \item {Responsible from over 60 students.}
        \item {Taking decisions and applying them to increase life standards.}
        \item {Ensure about the satisfaction of residences, parents, and university management.}
      \end{cvitems}
    }
    \cventry
  	{Teaching Assistant}
    {Momentum Learning}
    {Houston, TX, USA}
    {June 2017 - July 2017}
    {
      \begin{cvitems}
        \item {Worked with Mr.Zhang to teach Java Programming to 16 kids from 10 to 18.}
        \item {\textbf{Tools:} Java, Eclipse}
        \item {\textbf{GitHub Repository:} \href{https://github.com/BedirT/Momentum\_Java\_Class}{https://github.com/BedirT/Momentum\_Java\_Class}}
      \end{cvitems}
    }
    
    {
    %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }
\end{cventries}
